\documentclass[12pt,fleqn]{article}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 160mm
\renewcommand\baselinestretch{1.0}
\pagestyle {plain}
\newcounter{stepnum}
\title{$\int_{}^{}$n2gr8-PROJECT APPROVAL}
\author{Anthony Guirguis (guirguia) \\ Hoda Mohammadi (mohamh8) \\ Mikolaj Hrycko (hryckom)}

\begin {document}
\maketitle
\newpage

\section *{Introduction}		
Software will provide users with an online environment within which they can input mathematical expressions and equations, that will then be solved. The software will give assistance to anyone who needs help solving complex mathematical equations. A website will be created in order to offer a more user friendly experience as several tools used for the same purpose are not user friendly. The website will be easily accessible and allow anyone with the link to use it. Any advanced solution techniques that do not come initially with In2gr8, can easily be added on later after the base software is completed.

\section *{Importance} 
The problem is important to solve because there are many students and even instructors that need help in solving complex mathematical problems and there are not many resources out there that provide such services with an easy to use interface. The reimplementation will provide a web interface that makes its use much easier for users than the original project.

\section *{Stakeholders}	
The stakeholders of this project are the group members who are creating this software along with the users who use the website we plan on creating and the 3XA3 Staff including but not limited to professors and teaching assistants. Other potential stakeholders could be users who plan on learning from the open source code that we will provide or users who plan on further developing it.


\section *{Context} 
The plan for the environment is currently online on a website that users can use on their desktops through a browser. This website will be accessible by anyone with access to the link and can be used by students, professors, or anyone who needs assistance with a mathematical problem.


\end {document}
